---
title: "Dynamic report"
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, error = FALSE)
```

```{css}
body {
  font-family: "Trebuchet MS", "Gill Sans", sans-serif;
  background-color: #fffaf5;
  color: #2b2118;
  line-height: 1.7;
  margin: 0 auto;
  max-width: 900px;
  padding: 1.5rem;
}

h2, h3 {
  color: #9c3d10;
}

h2 {
  border-bottom: 3px solid #f0b27a;
  padding-bottom: 0.35rem;
}

p {
  font-size: 1rem;
}
```

```{r data-prep}
library(tidyverse)

csv_url <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vTfpj3N-gr781x29ItgF2DSBX9b2lNXM1nVEa-Ef4ltB-cjGV1t1G1WiWfZY6LAioGv_paJSzm64F7c/pub?gid=1567798230&single=true&output=csv"

logged_data <- read_csv(csv_url)

original_names <- names(logged_data)

latest_data <- logged_data %>%
  rename(
    timestamp = all_of(original_names[1]),
    platform = all_of(original_names[2]),
    ad_type = all_of(original_names[3]),
    ad_duration_seconds = all_of(original_names[4]),
    click_response = all_of(original_names[5]),
    time_of_day = all_of(original_names[6])
  ) %>%
  mutate(
    timestamp = as.POSIXct(timestamp, format = "%d/%m/%Y %H:%M:%S"),
    ad_duration_seconds = as.numeric(ad_duration_seconds),
    click_response = factor(click_response, levels = c("Yes", "No"))
  )

report_summary_values <- latest_data %>%
  summarise(
    total_ads_logged = n(),
    average_duration = mean(ad_duration_seconds, na.rm = TRUE),
    max_duration = max(ad_duration_seconds, na.rm = TRUE),
    yes_clicks = sum(click_response == "Yes", na.rm = TRUE),
    click_rate = mean(click_response == "Yes", na.rm = TRUE)
  )

platform_counts <- latest_data %>%
  separate_rows(platform, sep = ",\\s*") %>%
  count(platform, sort = TRUE)

ad_type_counts <- latest_data %>%
  separate_rows(ad_type, sep = ",\\s*") %>%
  count(ad_type, sort = TRUE)
```

## Tracking Online Advertising Patterns

This dynamic report summarises the advertising data collected through the Google Form and highlights the kinds of ads that appeared most often across different online platforms.

A total of `r report_summary_values$total_ads_logged` ads were logged in this dataset. The average ad duration was `r round(report_summary_values$average_duration, 1)` seconds, and the longest ad lasted `r report_summary_values$max_duration` seconds.

The ads were not equally persuasive. `r report_summary_values$yes_clicks` of the logged ads were attractive enough to click on, which gives a click rate of `r round(report_summary_values$click_rate * 100, 1)`%.

The most frequently observed platform was **`r platform_counts$platform[1]`**, with `r platform_counts$n[1]` observations. The most common ad type was **`r ad_type_counts$ad_type[1]`**, appearing `r ad_type_counts$n[1]` times.

### Ad Platforms

The first bar chart compares how often ads were observed on each platform. This helps show where online advertising appeared most frequently in the data collection period.

```{r platform-chart, fig.width=8, fig.height=4.8}
ggplot(platform_counts, aes(x = reorder(platform, n), y = n)) +
  geom_col(fill = "#355c7d") +
  coord_flip() +
  labs(
    title = "Number of observed ads by platform",
    x = "Platform",
    y = "Number of ads"
  ) +
  theme_minimal(base_size = 12)
```

### Ad Types

The second bar chart focuses on the content of the ads. It shows which ad categories appeared most often and helps identify the main kinds of products or services being promoted.

```{r ad-type-chart, fig.width=8, fig.height=4.8}
ggplot(ad_type_counts, aes(x = reorder(ad_type, n), y = n)) +
  geom_col(fill = "#c06c52") +
  coord_flip() +
  labs(
    title = "Number of observed ads by ad type",
    x = "Ad type",
    y = "Number of ads"
  ) +
  theme_minimal(base_size = 12)
```
