---
title: "Project 2"
author: "Nero Zhang"
subtitle: "STATS 220 Semester One, 2026"
output:
  html_document:
    code_folding: hide
    self_contained: true
---

## Introduction

The focus of my data collection for Project 2 was online advertising. Over several days, I repeatedly logged the ads that I saw while using different digital platforms, including YouTube, Instagram, TikTok, Facebook, and X. I was interested in tracking how often ads appeared across platforms, what kinds of products or services were being promoted, how long the ads were, whether they seemed attractive enough to click on, and what time of day they were observed. I chose this topic because online ads are a common part of everyday digital life, but they can also vary a lot depending on platform, timing, and content. Recording repeated observations over time made it possible to build a dataset that could be analysed for patterns rather than relying on a single example.

One guideline I considered when designing my Google Form was that questions should be clear and easy to answer quickly at the moment of observation. Because this project used observational logging, I needed a form that I could complete efficiently on my phone without losing track of what I had just seen. I therefore used short, direct question wording and included a mix of question types that matched the data I wanted to collect. For example, I used a numeric response for ad duration and categorical response options for platform, ad type, click response, and time of day. This helped keep the data tidy and easier to compare later in R.

The data collected allows me to learn meaningful things through analysis. By summarising the numeric values and graphing the categorical variables, I can compare which platforms showed the most ads, which ad types appeared most often, and whether ads with certain characteristics seemed more appealing. This makes the data useful for identifying patterns in my own online advertising experience rather than just listing isolated observations.

My Google Form responder link is here: [Online advertising observation form](https://docs.google.com/forms/d/19bOrj-yF1ZdTndxXNDd_PU7zPeoen1nMYsBfzHitFO8/viewform)

Form design and data collection for this project were completed by me.

## Dynamic report

My published dynamic report is available here: [GitHub Pages dynamic report](https://lateyoun9.github.io/stats220/)

This webpage is dynamic because it is connected to the published CSV version of my Google Sheet. As more observations are added through the Google Form, the underlying data changes, and the report updates when the page is reloaded. This means the report is not just a static summary of one fixed dataset. Instead, it is a live reporting system that can continue to reflect my online advertising observations over time. In the report, I used dynamic text to comment on summary values such as the total number of ads logged, the average duration of ads, and the proportion of ads that seemed attractive enough to click. I also included bar charts that compare the frequency of platforms and ad types so the report communicates both numerical summaries and visual patterns.

## Creativity

I think my project demonstrates creativity in several ways. First, I selected a data collection focus that is specific to my own everyday digital experience: the online ads that appear while I use different social media and video platforms. This gave the project a clear real-world context and made the observational logging process meaningful. Second, I designed the form so that it captured several different aspects of each ad, including platform, ad type, duration, click appeal, and time of day. This allowed me to build a richer dataset that could support more than one kind of comparison.

My project also shows creativity in how the results are presented. In my dynamic report, I did not only display raw counts. I wrote dynamic comments that interpret the data and explain what the charts show, which makes the report more informative for a reader. I also customised the appearance of the report with CSS so that it looks more polished and intentional than a default output. In addition, I used data cleaning and reshaping choices that helped me turn multiple-response observations into informative bar charts for platforms and ad types. Altogether, these choices helped produce a report that is more insightful and visually effective than a minimal basic submission.

## Learning reflection

One important idea I learned from Module 2 is that a report can be both reproducible and dynamic at the same time. Before this module, I mainly thought of reports as static documents that are written once and then finished. Through this project, I learned that an R Markdown report can pull data from a live online source, run code again, and generate updated output whenever the data changes. That idea helped me understand how data technologies connect data collection, storage, analysis, and communication into one workflow.

This project also made me more curious about other forms of web-based data communication. In the future, I would like to explore more advanced dashboards, interactive graphics, and ways to automate the updating of online reports. Because I completed this project individually, one group-work skill I want to keep developing is explaining my process clearly to other people. In future collaborative projects, I want to improve at dividing tasks early, checking in regularly, and making sure everyone has a shared understanding of the project goals and workflow.

## Appendix

```{r file='exploration.R', eval=FALSE, echo=TRUE}

```

```{r file='dynamic_report.Rmd', eval=FALSE, echo=TRUE}

```
